---
title: "Relatedness"
author: "Antonio Ortega Jiménez"
date: "June 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("ggvis")
library("ggplot2")
library("dplyr")
library("shiny")
data.dir <- "~/AthGene/data"
setwd(data.dir)
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

individuals.fl <- paste(data.dir, "individuals_athgene.txt", sep = "/")
people <- read.table(file = individuals.fl,
                     col.names = c("sample", "pop", "super", "gender", "batch"),
                     fill = T, header = T)
people$batch <- factor(people$batch)
#

genome.fl <- paste(data.dir, "maf0.05.genome", sep = "/")

genome <- read.table(file = genome.fl, header = T)

genome <- merge(genome, select(people, FID1 = sample, super), by = "FID1")
filter(genome, PI_HAT > 0.1) %>% nrow
genome %>% nrow


#genome %>% filter(Z2 == 1) %>% View
ggplot(data = genome,
       mapping = aes(x = Z1, y = Z2, col = super, alpha = PI_HAT)) +
  geom_point() +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_manual(values = cbPalette) +
  guides(alpha = FALSE)

ggsave("../plots/IBD.png")

#
genome.fl <- paste(data.dir, "athgene_relatives.genome", sep = "/")

genome <- read.table(file = genome.fl, header = T, stringsAsFactors = F)

genome <- merge(genome, select(people, FID1 = sample, super), by = "FID1")
filter(genome, PI_HAT > 0.1) %>% nrow
genome %>% nrow

#
#genome %>% filter(Z2 == 1) %>% View
visual_data <- filter(genome, PI_HAT > 0)





ggplot(data = filter(genome, PI_HAT > 0),
       mapping = aes(x = Z1, y = Z2, alpha = PI_HAT)) +
  geom_point(show.legend = F) +
  scale_x_continuous(limits = c(0, 1)) +
  scale_y_continuous(limits = c(0, 1)) +
  scale_color_manual(values = cbPalette) +
  guides(alpha = FALSE)

ggsave("../plots/IBD.png")



#
genome.fl <- paste(data.dir, "athgene_relatives.genome", sep = "/")

genome <- read.table(file = genome.fl, header = T, stringsAsFactors = F)

genome <- merge(genome, select(people, FID1 = sample, super), by = "FID1")


visual_data <- filter(genome, PI_HAT > 0.1)
visual_data$pair <- 
  paste(gsub(pattern = "(I)([0-9]*)", "\\2", x = visual_data$FID1),
        "+",
        gsub(pattern = "(I)([0-9]*)", x = visual_data$FID2, "\\2"),
        sep = "")


ggvis(data = visual_data, 
      ~Z1, ~Z2,
      opacity:= ~PI_HAT,
      key:= ~pair
) %>%
  layer_points() %>%
  add_tooltip(html = function(data) paste("Customers: ", data$pair),
              on = "hover")
